A meta-analysis of mental rotation ability in the first years of life

### 2022-04-14 code/analysis.Rmd
Fix profile plots
Rename `id` to `article`

# Overview of the different effect sizes
dat %>%
  select(id, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri) %>%
  print(n = Inf)

@@

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
    age_months = age_mean / 30.417
  ) %>%
  select(id, group, age_months, female_percent, ni, yi, sei) %>%
  # Compute sampling variance from standard errors
  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
  tibble() -> dat_r

# Create vector of experiment IDs for plotting
experiment_ids <- with(dat_r, paste(id, group, sep = ", "))

@@

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# # Profile likelihodd plots
# profile(res_mv, sigma2 = 1)
# profile(res_mv, sigma2 = 2)

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
```

@@

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | group / id),
  data = dat_r,
  prior = priors,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

@@

```{r}
length(unique(included$id))
```

@@

```{r}
included %>%
  uncount(1e4) %>%
  mutate(
    group_text = if_else(is.na(group), "NA", group),
    id_group = str_c(id, ", ", group_text),
    id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
    age_sd = if_else(!is.na(age_sd), age_sd, 10.),
    days = rnorm(n(), age_mean, age_sd),
    months = days / 30.417,
  ) %>%
  ggplot(aes(x = months, y = id_group_ordered, fill = female_percent)) +
  geom_density_ridges() +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = c(1, 20), expand = FALSE) +
  labs(x = "Age (m)", fill = "Percent\nfemale") +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 10)
  )
```

@@

# Generate random experiments
n_boys <- 1e3
n_girls <- 1e3
n_exps <- 100
dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
dat <- do.call(rbind.data.frame, dat)
dat$id <- paste0("exp_", 1:n_exps)

@@

# Fit 3 level meta-analysis
res_full <- metafor::rma.mv(
  d_infants, v_d_infants,
  # random = ~ id | id,
  data = dat,
  slab = id
)

@@

  # Generate random experiments
  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
  dat <- do.call(rbind.data.frame, dat)
  dat$id <- paste0("exp_", 1:n_exps)

@@

  # Fit meta-analysis
  res_full <- metafor::rma.mv(
    d_infants, v_d_infants,
    # random = ~ id | id,
    data = dat,
    slab = id
  )

@@

n_metas <- 100
metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
metas <- do.call(rbind.data.frame, metas)
metas$id <- paste0("meta_", 1:n_metas)

>>>>

# Overview of the different effect sizes
dat %>%
  select(
    article, group, yi_type, yi, d, d_z_t, d_z_diff, d_av, d_nov_pref, ri
  ) %>%
  print(n = Inf)

@@

```{r, compute_meta, echo=TRUE}
# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    sei = sqrt(((2 * (1 - r_assumed)) / ni) + (yi^2 / (2 * ni))),
    age_months = age_mean / 30.417
  ) %>%
  select(article, group, age_months, female_percent, ni, yi, sei) %>%
  # Compute sampling variance from standard errors
  escalc(yi = yi, sei = sei, ni = ni, data = .) %>%
  tibble() -> dat_r

# Create vector of experiment IDs for plotting
experiment_ids <- with(dat_r, paste(article, group, sep = ", "))

@@

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# # Profile likelihodd plots
# profile(res_mv, tau2 = 1)
# profile(res_mv, rho = 1)

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | article,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
```

@@

# Run Bayesian multilevel model
res_brm <- brm(
  yi | se(sei) ~ 1 + (1 | group / article),
  data = dat_r,
  prior = priors,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

@@

```{r}
length(unique(included$article))
```

@@

```{r}
included %>%
  uncount(1e4) %>%
  mutate(
    group_text = if_else(is.na(group), "NA", group),
    id_group = str_c(article, ", ", group_text),
    id_group_ordered = fct_reorder(id_group, age_mean, .desc = TRUE),
    age_sd = if_else(!is.na(age_sd), age_sd, 10.),
    days = rnorm(n(), age_mean, age_sd),
    months = days / 30.417,
  ) %>%
  ggplot(aes(x = months, y = id_group_ordered, fill = female_percent)) +
  geom_density_ridges() +
  scale_fill_distiller(palette = "RdYlBu") +
  coord_cartesian(xlim = c(1, 20), expand = FALSE) +
  labs(x = "Age (m)", fill = "Percent\nfemale") +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    text = element_text(family = "Helvetica", size = 10)
  )
```

@@

# Generate random experiments
n_boys <- 1e3
n_girls <- 1e3
n_exps <- 100
dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
dat <- do.call(rbind.data.frame, dat)
dat$article <- paste0("exp_", 1:n_exps)

@@

# Fit 3 level meta-analysis
res_full <- metafor::rma.mv(
  d_infants, v_d_infants,
  # random = ~ article | article,
  data = dat,
  slab = article
)

@@

  # Generate random experiments
  dat <- replicate(n_exps, generate_exp(n_boys, n_girls), simplify = FALSE)
  dat <- do.call(rbind.data.frame, dat)
  dat$article <- paste0("exp_", 1:n_exps)

@@

  # Fit meta-analysis
  res_full <- metafor::rma.mv(
    d_infants, v_d_infants,
    # random = ~ article | article,
    data = dat,
    slab = article
  )

@@

n_metas <- 100
metas <- replicate(n_metas, generate_meta(100, 100, 100), simplify = FALSE)
metas <- do.call(rbind.data.frame, metas)
metas$article <- paste0("meta_", 1:n_metas)
